Recalibrating Gravitational Wave Phenomenological Waveform Model

### 2023-10-02 src/tex/ms.tex
added responses

@@

To compute the loss functions, we have to choose NR waveforms for calculating the mismatch.
Originally, 19 NR simulations were used to calibrate IMRPhenomD \citep{khan2016frequency}; nine of these 
are from the SXS catalog \citep{boyle2019sxs} and 10 BAM simulations. 
As BAM waveforms are not publicly available, we cannot use a training set identical to the original work.
Instead, we take the same nine waveforms from the SXS catalog plus two additional waveforms which closely mimic
two of the low mass ratio BAM simulations. 
The remaining BAM simulations have no close SXS counterparts, and are therefore not included in the training set.
Our main results therefore uses 11 NR waveforms for calibration which are listed in Tab.~\ref{tab:q148}.
Additional NR waveforms which are used for further calibration are listed in Tab.~\ref{tab:q1248}.

@@

The correlation we observe between the mismatches and the waveform's parameters
can also be used to design more physical ansatz. For example, we see the
recalibration process struggles to improve in the regime where $\chi_{1}$ is
positive and $\chi_{2}$ is negative. This means there is a dependency between
the two spins that is not captured by the current ansatz. A systematic scheme that
incorporates our calibration method with waveform design will be handy in
constructing new waveform models in the future.

>>>>

\usepackage[normalem]{ulem}

@@

To compute the loss functions, we have to choose NR waveforms for calculating the mismatch.
Originally, 19 NR simulations were used to calibrate IMRPhenomD \citep{khan2016frequency}; nine of these 
are from the SXS catalog 
\footnote{We took the CoM-corrected waveforms with 4th-order extrapolation.} 
\citep{boyle2019sxs} and 10 BAM simulations. 
As BAM waveforms are not publicly available, we cannot use a training set identical to the original work.
Instead, we take the same nine waveforms from the SXS catalog plus two additional waveforms which closely mimic
two of the low mass ratio BAM simulations. 
The remaining BAM simulations have no close SXS counterparts, and are therefore not included in the training set.
Our main results therefore uses 11 NR waveforms for calibration which are listed in Tab.~\ref{tab:q148}.
Additional NR waveforms which are used for further calibration are listed in Tab.~\ref{tab:q1248}.

@@

The correlation we observe between the mismatches and the waveform's parameters
can also be used to design more physical ansatz. For example, we see the
recalibration process struggles to improve in the regime where $\chi_{1}$ is
positive and $\chi_{2}$ is negative. \kl{\sout{This means there is a dependency between
the two spins that is not captured by the current ansatz.}} A systematic scheme that
incorporates our calibration method with waveform design will be handy in
constructing new waveform models in the future.

\kl{We note that in comparison to the original IMRPhenomD calibration, we restricted the 
parameter space to $q\leq8$ and directly used NR waveform instead of hybridized SEOB-NR 
waveforms, which clearly put the original IMRPhemonD result in a 
disadvantage. We have tried to train the model using a set of training waveforms of the same 
intrinsic parameters, but with BAM waveforms replaced with SEOBNR waveforms. The result 
shows a marginal improvement, which corresponds to the stitching problem discussed before.
However, it is known that IMRPhenomD has a large inaccuracy in the large mass-ratio regime, 
and is rarely used in this region of parameter space. Hence, we focus on showing AD with 
gradient descent, as a general and robust method, can be used to further optimize models 
independent of the training waveforms used.}
